---
title: "Empiric Discordance"
output: html_document
date: "`r Sys.Date()`"
---

```{r, echo=FALSE, message=FALSE, fig.height=4.25}
library(dplyr, quietly = TRUE)
load(file = '~/Desktop/EHR/EHR work/RdataFiles/ASTs_AbxAdmin_blood_2017_2023_imputed_encs_flagged_WIDE_survival.Rdata')
load(file = '~/Desktop/EHR/EHR work/RdataFiles/ASTs_blood_2017_2023.Rdata')
astDF <- empDF %>%
   select(PERSON_ID, ORDER_DATE, RESULT_DATE, BUG) %>%
   left_join(y = astDF %>% select(PERSON_ID, ORDER_DATE, RESULT_DATE, BUG, CEFEPIME:DELAFLOXACIN),
             relationship='many-to-many',
             multiple = 'first',
             by = join_by(PERSON_ID, ORDER_DATE, RESULT_DATE, BUG))
astDF <- astDF %>% arrange(PERSON_ID, BUG, ORDER_DATE)
empDF <- empDF %>% arrange(PERSON_ID, BUG, ORDER_DATE)
load(file = '~/Desktop/EHR/EHR-mining/UsefulDataForCleaning/antibiotic_names/abbr_named.Rdata')
abbr <- c(abbr, setNames('No abx', 'No abx'))
site_names <- c("CHP" = 'Childrens', 
                "UPMCALT" = 'Altoona', 
                "UPMCBED" = 'Bedford', 
                "UPMCCHA" = 'Chatauqua', 
                "UPMCEAS" = 'East',
                "UPMCHAM" = 'Hamot', 
                "UPMCHZN" = 'Horizon',
                "UPMCJAM" = 'Jameson', 
                "UPMCLOC" = '', 
                "UPMCMCK" = 'McKeesport', 
                "UPMCMER" = 'Mercy', 
                "UPMCMUN" = '', 
                "UPMCMWH" = 'Magee-Womens', 
                "UPMCNOR" = 'Northwest', 
                "UPMCPAS" = 'Passavant', 
                "UPMCPUH" = 'Presbyterian', 
                "UPMCSHY" = 'Shadyside', 
                "UPMCSMH" = 'St. Margaret', 
                "UPMCSOL" = '', 
                "UPMCSUN" = '', 
                "UPMCWIL" = 'Williamsport')
site_names <- setNames(paste0(site_names, ' (', gsub('UPMC', '', names(site_names)), ')'), 
                       names(site_names))
w <- grep('^ ', site_names)
site_names[w] <- gsub(' \\(([A-Z]+)\\)', '\\1', site_names[w])

empDF <- empDF %>% mutate(SITE = site_names[FACILITY])

# mostly therapies staying concordant or going from discordant --> concordant
empDF %>% select(FLAGe, FLAGt) %>% table()


empDF <- empDF %>% mutate(X = as.numeric(lubridate::as.duration(ORDER_DATE - ADMIT_DATE)) / 86400)
empDF <- empDF %>% mutate(HOSP_ACQ = X >= 2)
empDF <- empDF %>% mutate(LOS = as.numeric(lubridate::as.duration(DISCHARGE_DATE - ADMIT_DATE)) / 86400)

los <- empDF$LOS
los <- los[!is.na(los)]
range(los)
hist(los, breaks=diff(range(los)), xlim=c(0,60), main='Length of stay', xlab='Days')
median(los) # 8.7 days
mean(los) # 14.7 days


x <- empDF$X
x <- x[!is.na(x)]
range(x)
hist(x,
     ylim = c(0, 600),
     breaks=diff(range(x)),
     main = 'ORDER - ADMISSION',
     xlab = 'Days')


cat(round(sum(x < 0) / length(x) * 100, 1), '% of blood cultures occur before admisssion', sep='')
cat(round(sum(x < -0.25) / length(x) * 100, 1), '% of blood cultures occur less than a quarter before admisssion', sep='')
cat(round(sum(x > 2) / length(x) * 100, 1), '% of blood cultures are hospital-acquired (> 48 hours after admission)', sep='') # 58%

t <- empDF %>%
   filter(!is.na(ADMIT_DAY)) %>%
   summarise(n = n(),
             ha = sum(HOSP_ACQ, na.rm=T) / n * 100,
             ca = sum(!HOSP_ACQ, na.rm=T) / n * 100,
             .by = BUG)

cat('Highest rates of hospital-acquired')
t %>% filter(n > 100L) %>% arrange(desc(ha))
cat('Rates of hospital-acquired ordered by total number')
t %>% arrange(desc(n))
cat('Highest rates of community-acquired (ignoring Streptococcus)')
t %>% filter(n > 100L) %>% arrange(desc(ca)) %>% filter(!grepl('Strepto', BUG))

cat('Rates of empiric concordance by hospital- vs. community-acquired')
empDF %>%
   summarise(total = n(),
             treated = sum(FLAGe != 'No abx given'),
             pcnt_treated = treated / total * 100,
             disc = sum(FLAGe == 'DISCORDANT') / treated * 100,
             conc = sum(FLAGe == 'CONCORDANT') / treated * 100,
             nott = sum(FLAGe == 'NOTTESTED') / treated * 100,
             .by = HOSP_ACQ)

t <- empDF %>% 
   filter(!is.na(ADMIT_DAY)) %>%
   filter(!grepl('+', FACILITY, fixed=TRUE)) %>%
   summarise(total = n(),
             treated = sum(FLAGe != 'No abx given'),
             disc = sum(FLAGe == 'DISCORDANT') / treated * 100,
             no_abx = sum(FLAGe == 'No abx given') / treated * 100,
             conc = sum(FLAGe == 'CONCORDANT') / treated * 100,
             nt = sum(FLAGe == 'NOTTESTED') / treated * 100,
             .by = SITE) %>%
   arrange(desc(total))
knitr::kable(t, digits=1)
```


```{r, echo=FALSE, message=FALSE, fig.height=4.25, eval=TRUE}
# # missing ASTs for concordance analysis
# empDF %>% 
#    filter(FLAG == 'NOTTESTED', BUG == 'Staphylococcus aureus') %>%
#    select(PERSON_ID, ORDER_DAY, FLAG, BUG, ABX) %>%
#    distinct() %>%
#    count(ABX, sort=TRUE)
# empDF %>% 
#    filter(FLAG == 'NOTTESTED', BUG == 'Staphylococcus aureus', ABX == 'AZITHROMYCIN') %>%
#    count(OXACILLIN, CLINDAMYCIN)




# combine multiple blood isolate cases
df <- empDF %>%
   group_by(PERSON_ID, ORDER_DAY) %>% mutate(MULT_BLOOD_ISO = n() > 1L) %>% ungroup() %>%
   select(PERSON_ID, ORDER_DAY, BUG, ABX_EMP, FLAGe, FLAGer, MULT_BLOOD_ISO) %>%
   summarise(ABX_EMP = list(unique(unlist(ABX_EMP))),
             BUG = paste0(sort(unique(BUG)), collapse=' + '),
             FLAGe = paste(sort(unique(FLAGe)), collapse=' + '),
             FLAGer = paste(sort(unique(FLAGer)), collapse=' + '),
             .by=c(PERSON_ID, ORDER_DAY, MULT_BLOOD_ISO))
df <- df %>%
   mutate(across(
      .cols = c(FLAGe, FLAGer),
      .fns = ~ case_when(
         grepl('+', ., fixed=TRUE) & grepl('DISCORDANT', .) ~ 'DISCORDANT',
         grepl('+', ., fixed=TRUE) & !grepl('DISCORDANT', .) & grepl('CONCORDANT', .) ~ 'CONCORDANT',
         . == 'No abx given + NOTTESTED' ~ 'NOTTESTED',
         .default = .
      )))
df %>% count(FLAGe)
n <- round(sum(df$FLAGe == 'No abx given') / nrow(df) * 100, 1)
c <- round(sum(df$FLAGe == 'CONCORDANT') / sum(df$FLAGe != 'No abx given') * 100, 1)
d <- round(sum(df$FLAGe == 'DISCORDANT') / sum(df$FLAGe != 'No abx given') * 100, 1)
nt <- round(sum(df$FLAGe == 'NOTTESTED') / sum(df$FLAGe != 'No abx given') * 100, 1)
cat(n, '% received no empiric therapy\n', sep='')
cat(c, '% concordant\n', sep='')
cat(d, '% discordant\n', sep='')
cat(nt, '% not tested\n', sep='')

df %>% count(FLAGe, FLAGer, sort=TRUE)

#sw <- round(sum(df$FLAGe == 'DISCORDANT' & df$FLAGer == 'CONCORDANT') / sum(df$FLAGe == 'DISCORDANT') * 100, 1)
sw <- round(sum(df$FLAGe == 'DISCORDANT' & df$FLAGer == 'CONCORDANT') / sum(df$FLAGe != 'No abx given') * 100, 1)
cat (sw, '% of those called discordant MIGHT be concordant if time stamp issue didnt exist\n', sep='')

#sw <- round(sum(df$FLAGe == 'No abx given' & df$FLAGer != 'No abx given') / sum(df$FLAGe == 'No abx given') * 100, 1)
sw <- round(sum(df$FLAGe == 'No abx given' & df$FLAGer != 'No abx given') / nrow(df) * 100, 1)
cat (sw, '% of those called no abx given MIGHT have received empiric treatment if time stamp issue didnt exist\n', sep='')




# multi-clonal infections have twice the rate of discordance
t <- df %>% select(FLAGe, MULT_BLOOD_ISO) %>% table()
t <- apply(t, 2, function(x) round(x / sum(x) * 100, 1))
print(t)


t <- empDF %>%
   summarise(total=n(),
             treated = sum(FLAGe != 'No abx given'),
             conc = sum(FLAGe == 'CONCORDANT'),
             disc = sum(FLAGe == 'DISCORDANT'),
             nt = sum(FLAGe == 'NOTTESTED'),
             no = sum(FLAGe == 'No abx given'),
             .by=BUG) %>%
   mutate(across(c(disc, nt, conc), ~ . / treated * 100),
          no = no / total * 100)

cat('DISCORDANCE STATS')
cat('Organized by total')
t %>% arrange(desc(total))
cat('Organized by rates of no treatment')
t %>% filter(total > 100L) %>% arrange(desc(no))
cat('Organized by rates of discordance')
t %>% filter(total > 100L) %>% arrange(desc(disc)) %>% print(n=12)
cat('Organized by rates of concordance')
t %>% filter(total > 100L) %>% arrange(desc(conc)) %>% print(n=12)
cat('Organized by rates of not tested')
t %>% filter(total > 100L) %>% arrange(desc(nt)) %>% print(n=12)



# old
#### Empiric discordance relative to recency of antibiotic prescriptions ####
{
   # empDF %>%
   #    mutate(prv_abx = !is.na(DAYS_SINCE_MOST_RECENT_ABX)) %>%
   #    summarise(sum(FLAGe == 'DISCORDANT') / n(),
   #              .by = prv_abx)
   # t <- empDF %>%
   #    mutate(prv_abx = case_when(
   #       DAYS_SINCE_MOST_RECENT_ABX > 14L ~ '> 2w',
   #       DAYS_SINCE_MOST_RECENT_ABX > 7L & DAYS_SINCE_MOST_RECENT_ABX <= 14L ~ '1-2w',
   #       DAYS_SINCE_MOST_RECENT_ABX <= 7L & DAYS_SINCE_MOST_RECENT_ABX > 1L ~ '1w',
   #       DAYS_SINCE_MOST_RECENT_ABX == 1L ~ '1d',
   #       is.na(DAYS_SINCE_MOST_RECENT_ABX) ~ '> 1m'
   #    )) %>%
   #    summarise('discordant' = sum(FLAGe == 'DISCORDANT') / n(),
   #              'concordant' = sum(FLAGe == 'CONCORDANT') / n(),
   #              'no empiric abx' = sum(FLAGe == 'No empiric therapy given') / n(),
   #              'not tested' = sum(FLAGe == 'NOT TESTED') / n(),
   #              .by = prv_abx) %>%
   #    arrange(discordant)
   # n <- t$prv_abx
   # t <- as.matrix(t[-1])
   # rownames(t) <- n
   # t <- t(t)
   # b <- barplot(t, plot=FALSE)
   # y <- cumsum(c(0, t[,ncol(t)]))
   # y <- y[-1] - diff(y) / 2
   # 
   # par(mar=c(3.5,3,3,6), mgp=c(2, 0.5, 0), tck=-0.015)
   # barplot(t, xlab='Last antibiotic administration')
   # text(x=b[length(b)]+0.6, y=y, adj=0, labels=rownames(t), xpd=NA)
}


###################################
#### Time to first concordance ####
###################################
xlim <- c(-48, 72)
ylim <- c(0, 10500)
col_vec <- c('#FF000055', '#0000FF55')
hist(empDF$TIME_TO_FIRST_ABX, breaks=diff(range(empDF$TIME_TO_FIRST_ABX, na.rm=T)), ylim=ylim, xpd=NA,
     xlim=xlim, col=col_vec[1], main='Timing of first antibiotic therapy', xlab='Hours')
hist(empDF$TIME_TO_CONC, breaks=diff(range(empDF$TIME_TO_CONC, na.rm=T)), add=TRUE, col=col_vec[2])
legend('topright', legend=c('first antibiotic', 'first concordant'), xpd=NA,
       pch=15, col=col_vec, pt.cex = 2.5)

hist(empDF$TIME_TO_FIRST_ABX_STRICT, breaks=diff(range(empDF$TIME_TO_FIRST_ABX_STRICT, na.rm=T)), ylim=ylim, xpd=NA,
     xlim=xlim, col=col_vec[1], main='Timing of first antibiotic therapy\n-remove missing time stamps', xlab='Hours')
hist(empDF$TIME_TO_CONC_STRICT, breaks=diff(range(empDF$TIME_TO_CONC_STRICT, na.rm=T)), add=TRUE, col=col_vec[2])
legend('topright', legend=c('first antibiotic', 'first concordant'), xpd=NA,
       pch=15, col=col_vec, pt.cex = 2.5)


n <- sum(!is.na(empDF$TIME_TO_FIRST_ABX)) / 100
sum(empDF$TIME_TO_CONC < -48, na.rm=T) / n # 0%
sum(empDF$TIME_TO_CONC < -24, na.rm=T) / n # 2.0%
sum(empDF$TIME_TO_CONC < 0, na.rm=T) / n    # 30.8%
sum(empDF$TIME_TO_CONC < 24, na.rm=T) / n   # 83%
sum(empDF$TIME_TO_CONC >= 24, na.rm=T) / n   # 13.4%
sum(empDF$TIME_TO_CONC >= 48, na.rm=T) / n   # 6.4%
sum(empDF$TIME_TO_CONC >= 72, na.rm=T) / n   # 2.9%
sum(empDF$TIME_TO_CONC >= 96, na.rm=T) / n   # 1.6%
(sum(is.na(empDF$TIME_TO_CONC)) - sum(is.na(empDF$TIME_TO_FIRST_ABX))) / n # 3.6%

n <- sum(!is.na(empDF$TIME_TO_FIRST_ABX_STRICT)) / 100
sum(empDF$TIME_TO_CONC_STRICT < -48, na.rm=T) / n # 0%
sum(empDF$TIME_TO_CONC_STRICT < -24, na.rm=T) / n # 1.3%
sum(empDF$TIME_TO_CONC_STRICT < 0, na.rm=T) / n    # 7.5%
sum(empDF$TIME_TO_CONC_STRICT < 24, na.rm=T) / n   # 82%
sum(empDF$TIME_TO_CONC_STRICT >= 24, na.rm=T) / n   # 13.9%
sum(empDF$TIME_TO_CONC_STRICT >= 48, na.rm=T) / n   # 6.6%
sum(empDF$TIME_TO_CONC_STRICT >= 72, na.rm=T) / n   # 3.1%
sum(empDF$TIME_TO_CONC_STRICT >= 96, na.rm=T) / n   # 1.6%
(sum(is.na(empDF$TIME_TO_CONC_STRICT)) - sum(is.na(empDF$TIME_TO_FIRST_ABX_STRICT))) / n # 3.9%

```

```{r, fig.width=8.5, fig.height=5, eval=TRUE}
makeBarplot <- function(bug, drug, strict=FALSE) {
   col_vec <- c('S' = '#0000FF99', 'R' = '#FF000099')
   if (strict) {
      r <- empDF$TIME_TO_CONC_STRICT[empDF$BUG == bug & empDF[[drug]] == 1L]
      s <- empDF$TIME_TO_CONC_STRICT[empDF$BUG == bug & empDF[[drug]] == 0L]  
   } else {
      r <- empDF$TIME_TO_CONC[empDF$BUG == bug & empDF[[drug]] == 1L]
      s <- empDF$TIME_TO_CONC[empDF$BUG == bug & empDF[[drug]] == 0L]
   }
   if (length(r) == 0 | length(s) == 0) {
      plot.new()
      return()
   }
   med_diff <- median(r, na.rm=T) - median(s, na.rm=T)
   r[r < 0] <- 0
   s[s < 0] <- 0
   r[r > 72] <- 72
   s[s > 72] <- 72
   hist(s, breaks=diff(range(s, na.rm=T)), xlim=c(0, 72), xaxt='n', xlab='Days (relative to blood culture)', 
        main=paste0(round(med_diff, 1), ' hours'), border=NA, col=col_vec['S'], cex.main=1)
   hist(r, breaks=diff(range(r, na.rm=T)), add=TRUE, border=NA, col=col_vec['R'])
   abline(v = c(median(s, na.rm=T), median(r, na.rm=T)), lty=2, lwd=2, col=col_vec)
   axis(side=1, at=seq(-24,72,24), labels=-1:3)
   axis(side=1, at=seq(-24,72,6), labels=rep('', length(seq(-24,72,6))))
   legend('topright', title=stringr::str_to_sentence(drug), legend=c('S', 'R'), col=col_vec, pch=15, pt.cex=2, bty='n')
}


par(mfrow=c(1,2), mgp=c(1.75, 0.5, 0), mar=c(5,3,2,1), oma=c(0,0,2,0))
bugs <- c('Enterococcus faecium' = 'VANCOMYCIN', 
          'Staphylococcus aureus' = 'OXACILLIN',
          'Escherichia coli' = 'ESBL', 
          'Klebsiella pneumoniae' = 'ESBL',
          'Pseudomonas aeruginosa' = 'ESBL',
          'Enterococcus faecalis' = 'RIFAMPIN', 
          'Pseudomonas aeruginosa' = 'CIPROFLOXACIN',
          'Serratia marcescens' = 'ESBL',
          'Enterobacter cloacae' = 'PIPERACILLIN/TAZOBACTAM')
print('Time shown under each title is median(time to conc for resistant isolates) - median(time to conc for susceptible isolates)')
for (i in seq_along(bugs)) {
   bug <- names(bugs)[i]
   drug <- bugs[i]
   makeBarplot(bug, drug)
   makeBarplot(bug, drug, strict=TRUE)
   mtext(text=paste0('Time to first concordant therapy - ', names(bugs)[i]),
         side=3, line=-0.5, outer=TRUE, xpd=NA, at=0.5, font=4)
}


bug <- c('Staphylococcus aureus', 'Escherichia coli', 'Klebsiella pneumoniae', 'Pseudomonas aeruginosa',  'Enterococcus faecium', 'Proteus mirabilis', 'Enterobacter cloacae')
drug <- c('OXACILLIN',            'ESBL',             'ESBL',                  'PIPERACILLIN/TAZOBACTAM', 'VANCOMYCIN',           'ESBL',              'ESBL')
df <- tibble()
for (i in seq_along(bug)) {
   b <- bug[i]
   d <- drug[i]
   w <- which(empDF$BUG == b & !is.na(empDF[[d]]) & !is.na(empDF$TIME_TO_CONC_STRICT))
   df <- rbind(df, empDF[w,] %>% select(!!d, TIME_TO_CONC_STRICT) %>% rename(drug = !!d))
   # w <- which(empDF$BUG == b & !is.na(empDF[[d]]) & !is.na(empDF$disc) & empDF$FLAGe %in% c('CONCORDANT', 'DISCORDANT'))
   # df <- rbind(df, empDF[w,] %>% select(time, status, !!d, disc) %>% rename(drug = !!d))
}

col_vec <- c('S' = '#0000FF99', 'R' = '#FF000099')
r <- df$TIME_TO_CONC_STRICT[df$drug == 1L]
s <- df$TIME_TO_CONC_STRICT[df$drug == 0L]  

med_diff <- median(r, na.rm=T) - median(s, na.rm=T)
# r[r < 0] <- 0
# s[s < 0] <- 0
# r[r > 72] <- 72
# s[s > 72] <- 72
hist(s, breaks=diff(range(s, na.rm=T)), xlim=c(-12, 72), xaxt='n', xlab='Days (relative to blood culture)', 
     main='Bacteremia (common pathogens)\nTime to concordant therapy: ', border=NA, col=col_vec['S'], cex.main=1)
text(x=18, y=2000, adj=0, labels=paste0('Difference: ', round(med_diff, 1), ' hours'))
hist(r, breaks=diff(range(r, na.rm=T)), add=TRUE, border=NA, col=col_vec['R'])
abline(v = c(median(s, na.rm=T), median(r, na.rm=T)), lty=2, lwd=2, col=col_vec)
axis(side=1, at=seq(-24,72,24), labels=-1:3)
axis(side=1, at=seq(-24,72,6), labels=rep('', length(seq(-24,72,6))))
legend('topright', legend=c('S', 'R'), col=col_vec, pch=15, pt.cex=2, bty='n')
```


```{r, fig.height=7.5, fig.width=8, eval=TRUE}
###########################################################
#### Empiric therapies / rates of discordance - BY BUG ####
###########################################################
empDF$EMP_ABBR <- sapply(empDF$ABX_EMP, function(x) paste(abbr[x], collapse='+'))

makeFlagPlot <- function(e, main='', leg=FALSE, d) {
   pcnt_disc <- round(d['DISCORDANT'] / sum(d), 3) * 100
   
   abx <- e$EMP_ABBR
   total <- nrow(e)
   
   w_noAbx_inpt <- which(abx == '' & !is.na(e$ADMIT_DAY))
   w_noAbx_noInpt <- which(abx == '' & is.na(e$ADMIT_DAY))
   
   abx[w_noAbx_inpt] <- 'No abx (inpt)'
   abx[w_noAbx_noInpt] <- 'No abx (no inpt)'
   no_abx <- c('No abx (inpt)', 'No abx (no inpt)')
   
   h <- table(abx, e$FLAGe) / total * 100
   h <- h[order(rowSums(h), decreasing=TRUE), ]
   no_abx <- no_abx[no_abx %in% rownames(h)]
   if (length(no_abx) > 0) {
      x <- h[no_abx, ]
      h <- h[!rownames(h) %in% no_abx, ]
   }
   
   n <- min(c(12, nrow(h)))
   h <- t(head(h, n))
   if (!'NOTTESTED' %in% rownames(h)) h <- rbind(h, 0); rownames(h)[nrow(h)] <- 'NOTTESTED'
   h <- h[c('DISCORDANT', 'CONCORDANT', 'NOTTESTED', 'No abx given'), ]
   h <- cbind(h, t(x))
   
   b <- barplot(h, horiz=TRUE, names.arg=rep('', ncol(h)), legend=leg, xpd=NA, xaxt='n', font.main=4, xlab='%',
                col = gray.colors(n=4, start=0.2, end=0.92), xlim=c(0, 30), space=c(rep(0.1, n), 0.4, 0.1),
                main=paste0(main, '\n(n = ', prettyNum(total, big.mark=','), ' - ', pcnt_disc, '% discordant)'))
   axis(side=2, at=b, labels=colnames(h), las=1, tick=F)
   axis(side=1)
   text(x = colSums(h) + max(h)*0.01, y = b, adj = 0, xpd=NA, labels = round(colSums(h), 1))
}

PlotBug <- function(bug, drug) {
   bug_abbr <- gsub('^([A-Z])[a-z]+ ([a-z]+)$', '\\1_\\2', bug)
   bug_abbr_main <- gsub('_', '\\. ', bug_abbr)
   drug_abbr <- abbr[drug]
   if (drug == 'ESBL') drug_abbr <- drug
   cat(bug, '-', drug, '\n')
   
   e <- empDF %>% filter(BUG == bug) %>% mutate(!!drug := ifelse(is.na(get(drug)), -1, get(drug)))
   t <- e %>% filter(FLAGe != 'No abx given') %>% select(FLAGe, !!drug) %>% table()
   if (ncol(t) == 1) return()
   
   par(mar=c(2,7,3,4))
   makeFlagPlot(e=e, main=bug_abbr_main, leg=TRUE, d=rowSums(t))
   csums <- colSums(t)
   par(mar=c(2,7,3,0))
   if (csums['0'] > 20L) {
      makeFlagPlot(e=e %>% filter(get(drug) == 0L), main=paste0(bug_abbr_main, ' ', drug_abbr, '-S'), d=t[,'0']) 
   } else {
      plot.new()
   }
   if (csums['1'] > 20L) {
      makeFlagPlot(e=e %>% filter(get(drug) == 1L), main=paste0(bug_abbr_main, ' ', drug_abbr, '-R'), d=t[,'1']) 
   } else {
      plot.new()
   }
}

layout(matrix(c(1,1,2,3), nrow=2, byrow=T))
par(mgp=c(1.5, 0.5, 0), oma=c(2,0,2,0))
bugs <- c('Enterococcus faecium' = 'VANCOMYCIN', 
          'Staphylococcus aureus' = 'OXACILLIN',
          'Escherichia coli' = 'ESBL', 
          'Klebsiella pneumoniae' = 'ESBL',
          'Pseudomonas aeruginosa' = 'CEFTRIAXONE',
          'Enterococcus faecalis' = 'RIFAMPIN', 
          'Pseudomonas aeruginosa' = 'CIPROFLOXACIN',
          'Serratia marcescens' = 'ESBL',
          'Enterobacter cloacae' = 'PIPERACILLIN/TAZOBACTAM')
for (b in seq_along(bugs)) {
   bug <- names(bugs)[b]
   drug <- unname(bugs[b])
   PlotBug(bug, drug)
}
```

<br>
<br>
<br>

#### This section describes the relationship between the ***extent*** of resistance and the likelihood of receiving discordant empiric therapy

The x-axis for the following plots is one of the following:

* **absolute number** of antibiotics to which an isolate was **measured** resistant
* **proportion** of antibiotics to which an isolate was **measured** resistant
* **absolute number** of antibiotics to which an isolate was **imputed** to be resistant
* **proportion** of antibiotics to which an isolate was **imputed** resistant

The y-axis shows the proportion that isolates with the given ***extent*** of resistance received discordant therapy. The caveat is that this number is likely underestimated, potentially by as much as the proportion for which we could not make a concordant/discordant judgement due to lack of knowledge about an isolate's resistance profile. We call this "unknown" and it is shown in <span style="color:red;">red</span>.


```{r, echo=FALSE, fig.height=7, eval=TRUE}
#################################################
###### LEVEL OF RESISTANCE VS. DISCORDANCE ######
#################################################
common_bugs <- c("Escherichia coli", "Staphylococcus aureus", "Klebsiella pneumoniae", 
                 "Enterococcus faecalis", "Pseudomonas aeruginosa", "Proteus mirabilis", 
                 "Enterococcus faecium", "Enterobacter cloacae", "Streptococcus pneumoniae", 
                 "Streptococcus agalactiae", "Serratia marcescens", "Klebsiella oxytoca", 
                 "Streptococcus mitis", "Viridans Streptococci", "Streptococcus pyogenes", 
                 "Streptococcus anginosus", "Morganella morganii", "Klebsiella aerogenes", 
                 "Acinetobacter baumannii")
wE <- empDF$BUG %in% common_bugs
wA <- astDF$BUG %in% common_bugs
if (!all(wE == wA)) {
   print('DATA FRAMES ARE DANGEROUSLY DIFFERENT!!')
   break
}

empDF <- empDF[wE, ]
astDF <- astDF[wE, ]



getDF <- function(df, flags, prop=FALSE, i=FALSE) {
   if (prop) {
      t <- apply(df %>% select(CEFEPIME:DELAFLOXACIN), 1, function(x) sum(x, na.rm=T) / sum(!is.na(x), na.rm=T))
      t[t >= 0   & t < 0.05] <- 0
      t[t >= 0.05 & t < 0.1] <- 0.05
      t[t >= 0.1 & t < 0.15] <- 0.1
      t[t >= 0.15 & t < 0.2] <- 0.15
      t[t >= 0.2 & t < 0.25] <- 0.2
      t[t >= 0.25 & t < 0.3] <- 0.25
      t[t >= 0.3 & t < 0.35] <- 0.3
      t[t >= 0.35 & t < 0.4] <- 0.35
      t[t >= 0.4 & t < 0.45] <- 0.4
      t[t >= 0.45 & t < 0.5] <- 0.45
      t[t >= 0.5 & t < 0.55] <- 0.5
      t[t >= 0.55 & t < 0.6] <- 0.55
      t[t >= 0.6 & t < 0.65] <- 0.6
      t[t >= 0.65 & t < 0.7] <- 0.65
      t[t >= 0.7 & t < 0.75] <- 0.7
      t[t >= 0.75 & t < 0.8] <- 0.75
      t[t >= 0.8 & t < 0.85] <- 0.8
      t[t >= 0.85 & t < 0.9] <- 0.85
      t[t >= 0.9 & t < 0.95] <- 0.9
      t[t >= 0.95   & t < 1] <- 0.95
   } else {
      t <- apply(df %>% select(CEFEPIME:DELAFLOXACIN), 1, function(x) sum(x, na.rm=T))
   }
   w <- which(is.na(t))
   if (length(w) > 0) {
      t <- t[-w]
      flags <- flags[-w]  
   }
   t <- table(t, flags)
   if (any(colnames(t) == 'No abx given')) {
      t <- t[, colnames(t) != 'No abx given']
   }
   n <- rowSums(t)
   w <- which(n >= 10L)
   n <- n[w]
   t <- t[w,]
   t <- apply(t, 1, function(x) x / sum(x))
   t <- as.data.frame(t(t))
   return(list(n=n, t=t))
}

makePlot <- function(t, xlab='', prop=FALSE, max_height, ylab=TRUE, num_bugs=TRUE, leg=FALSE) {
   pch <- 16
   cex = 0.9
   xvals <- as.numeric(rownames(t$t))
   if (prop)  xlim <- c(-0.05, 1.05)
   if (!prop) xlim <- c(-0.5, max(xvals)+0.5)
   plot(x = xvals,
        y = t$t$DISCORDANT,
        pch = pch, cex = cex,
        xlim = xlim,
        xaxs='i', xaxt='n',
        ylim = c(0, 1), yaxt = 'n',
        ylab='', xlab='')
   title(xlab=xlab, line=1.4)
   if (prop)  axis(side=1, at=seq(0, 1, 0.2))
   if (!prop) axis(side=1, at=0:max(xvals))
   if (ylab) {
      title(ylab='Proportion discordant', xpd=NA)
      axis(side=2, at=seq(0,1,0.2), las=1)
   }
   lines(x=xvals, y=t$t$DISCORDANT, lwd=0.5)
   #points(x=xvals, y=t$t$NOTTESTED, pch=pch, cex=cex, col='red')
   #lines(x=xvals, y=t$t$NOTTESTED, col='red')
   #if (leg) legend('topleft', inset=c(0.025, 0), bty='n', pt.cex=cex, legend=c('discordant', 'unknown'), pch=16, col=c('black', 'red'), lty=1)
   
   par(new=TRUE)
   bar_col <- '#000000'
   bar_width <- ifelse(prop, 0.025, 0.5)
   bar_heights <- t$n / max_height
   rect(xleft = xvals - bar_width,
        xright = xvals + bar_width,
        ybottom = 0,
        ytop = bar_heights,
        border=NA,
        col = paste0(bar_col, '22'))
   if (num_bugs) {
      sc_fac <- 10^(length(unlist(strsplit(as.character(max_height), '')))-1)
      s <- seq(0, floor(max_height/sc_fac)*sc_fac, sc_fac)
      axis(side=4, las=1, col=paste0(bar_col, '66'), col.axis=paste0(bar_col, '66'),
           at=seq(0, s[length(s)]/max_height, length.out=length(s)), 
           labels=s)
      mtext(side=4, line=2.5, text='Number of isolates', cex=par('cex.lab')-0.15, col=paste0(bar_col, '66'))
   }
}


toa <- getDF(astDF, empDF$FLAGe)
top <- getDF(astDF, empDF$FLAGe, prop=TRUE)
tia <- getDF(empDF, empDF$FLAGe, i=T)
tip <- getDF(empDF, empDF$FLAGe, prop=TRUE, i=T)
max_height <- max(c(toa$n, top$n, tia$n, tip$n))



# overall plots
par(mfrow=c(2,2), mar=c(2.5, 0.5, 0.5, 0.5), oma=c(5,3,2,3.5), mgp=c(1.7, 0.3, 0), tck=-0.01)
makePlot(toa, 'number of resistance phenotypes', max_height=max_height, leg=T, num_bugs=T)
plot.new()
plot.new()
plot.new()

makePlot(toa, 'measured (absolute number)', max_height=max_height, leg=T, num_bugs=F)
makePlot(top, 'measured (proportion - binned)', prop=TRUE, ylab=F, max_height=max_height)
makePlot(tia, 'imputed (absolute number)', max_height=max_height, num_bugs=F)
makePlot(tip, 'imputed (proportion - binned)', prop=TRUE, ylab=F, max_height=max_height)
mtext(side=3, at=0.5, text='All pathogens', outer=TRUE, line=0, xpd=NA, font=2)



# bug-specific plots
makeBugPlots <- function(bug) {
   a <- astDF[astDF$BUG == bug, ]
   e <- empDF[empDF$BUG == bug, ]
   f <- empDF$FLAGe[empDF$BUG == bug]
   toa <- getDF(a, f)
   top <- getDF(a, f, prop=T)
   tia <- getDF(e, f, i=T)
   tip <- getDF(e, f, prop=T, i=T)
   max_height <- max(c(toa$n, top$n, tia$n, tip$n))
   makePlot(toa, 'abs. number measured', max_height=max_height,                  ylab=T, num_bugs=F, leg=T)
   makePlot(top, 'fraction measured (binned)', prop=TRUE, max_height=max_height, ylab=F, num_bugs=T)
   makePlot(tia, 'abs. number imputed', max_height=max_height,                   ylab=T, num_bugs=F)
   makePlot(tip, 'fraction imputed (binned)', prop=TRUE, max_height=max_height,  ylab=F, num_bugs=T)
   mtext(side=3, at=0.5, text=bug, outer=TRUE, line=0, xpd=NA, font=2)
}

par(mfrow=c(2,2), mar=c(2.5, 0.5, 0.5, 0.5), oma=c(5,3,2,3.5), mgp=c(1.7, 0.3, 0), tck=-0.01)
for (bug in common_bugs) {
   print(bug)
   makeBugPlots(bug)
}



par(mfrow=c(1,1), mar=c(5, 5, 5, 5), oma=c(0,0,0,0), mgp=c(1.7, 0.3, 0), tck=-0.01)
# extent of resistance vs. time to concordance
R <- apply(astDF %>% select(CEFEPIME:DELAFLOXACIN), 1, function(x) sum(x, na.rm=T))

f <- function(r) {
   t <- table(R >= r, empDF$TIME_TO_CONC_STRICT >= 24)
   f <- fisher.test(t)
   if (f$p.value > 0.01) return(NA)
   return(c(f$estimate, f$conf.int))
}

t <- sapply(1:12, f)
plot(NA, xlim=c(1,12), ylim=c(1, max(t)), log='y',
     , ylab='Odds ratio', xlab='Number of resistance phenotypes', main='Resistance increases likelihood of\n> 24 hour delay to concordant therapy')
points(x=1:12, y=t[1,], pch=16)
arrows(x0=1:12, y0=t[2,], y1=t[3,], code=3, angle=90, length=0.05)
```











