---
title: "MSThesisAppendix"
author: 'Samuel Blechman'
date: "`r Sys.Date()`"
output: 
   html_document:
      toc: true
      toc_depth: 4
      toc_float:
         collapsed: true
---


```{r, echo=FALSE}
library(knitr)
library(kableExtra)
library(DiagrammeR)
```
<br />
<br />



### Table 1. List of antibiotic names and abbreviations.
```{r, echo=FALSE, out.width='500pt', fig.align='left'}
load(file='~/Desktop/EHR-mining/UsefulDataForCleaning/antibiotic_names/abx_abbr_matrix.Rdata')
kable(abx_mat, "html", escape = TRUE) %>%
   kable_styling(full_width = FALSE, position='left')
```
<br />
<br />



### Table 2. List of antibiotic groupings and corresponding antibiotic names.
```{r, echo=FALSE, out.width='500pt', fig.align='left'}
load(file='~/Desktop/EHR-mining/BuildCohortDatasets/OtherScriptsAndData/abx_groupings_matrix.Rdata')
kable(abx_mat, "html", escape = TRUE) %>%
   kable_styling(full_width = FALSE, position='left') %>%
   column_spec(2, width = "30em", extra_css = "word-wrap: break-word;")
```
<br />
<br />



### Table 3. List of pathogens.
```{r, echo=FALSE, out.width='500pt', fig.align='left'}
load(file='~/Desktop/EHR-mining/UsefulDataForCleaning/bug_group_matrix.Rdata')
kable(bug_mat, "html", escape = TRUE) %>%
   kable_styling(full_width = FALSE, position='left') %>%
   column_spec(2, width = "40em", extra_css = "word-wrap: break-word;")
```
<br />
<br />



### Table 4. List of UPMC facilities and facility cateogories.
```{r, echo=FALSE, out.width='500pt', fig.align='left'}
load(file = '~/Desktop/EHR-mining/UsefulDataForCleaning/facility_category_matrix.Rdata')
kable(fac_mat, "html", escape = TRUE) %>%
   kable_styling(full_width = FALSE, position='left') %>%
   column_spec(2, width = "30em")
```
<br />
<br />



### Table 5. Comorbidity covariates and corresponding ICD-10 code(s).
```{r, echo=FALSE, out.width='500pt', fig.align='left'}
load(file='~/Desktop/EHR-mining/UsefulDataForCleaning/ICDcodes_covariates_matrix.Rdata')
kable(mat, "html", escape = TRUE) %>%
   kable_styling(full_width = FALSE, position='left') %>%
   column_spec(2, width = "40em", extra_css = "word-wrap: break-word;")
```
<br />
<br />



### Figures 1-8. Cohort exclusion filtering sample sizes.
```{r, echo=FALSE, out.width='425pt', fig.align='left'}
build_flowchart <- function(steps_df, final_split = NULL, title = NULL) {
   nodes <- ""
   edges <- ""
   final_split <- rev(final_split)
   
   # Define nodes
   for (i in seq_len(nrow(steps_df))) {
      id <- paste0("Step", i)
      lbl <- paste0(steps_df$label[i], "\n(n = ", steps_df$n[i], ")")
      fill <- if (i == 1 || i == nrow(steps_df)) "lightblue" else "lightgray"
      nodes <- paste0(
         nodes,
         id, ' [label = "', lbl, '", shape = box, style = filled, fillcolor = ', fill, '];\n'
      )
      if (i > 1) {
         edges <- paste0(edges, "Step", i - 1, " -> Step", i, ";\n")
      }
   }
   
   # Final split into treatment groups
   if (!is.null(final_split)) {
      i <- nrow(steps_df)
      for (j in seq_along(final_split)) {
         id <- paste0("Group", j)
         lbl <- paste0(names(final_split)[j], "\n(n = ", final_split[j], ")")
         nodes <- paste0(
            nodes,
            id, ' [label = "', lbl, '", shape = ellipse, style = filled, fillcolor = pink];\n'
         )
         edges <- paste0(edges, "Step", i, " -> ", id, ";\n")
      }
   }
   
   # Wrap in grViz syntax
   dot <- paste0(
      "digraph flowchart {\n",
      #paste0("  graph [layout = dot, rankdir = TB, label = ", title, ", labelloc = t, fontsize = 24];\n"),
      paste0("  graph [layout = dot, rankdir = TB];\n"),
      "  node [fontname = Helvetica];\n",
      nodes,
      edges,
      "}"
   )
   
   # grViz(dot)
   htmltools::div(
      grViz(dot, width=600, height=900),
      # style = "margin-top: 40px; margin-bottom: 60px;"
   )
}

load(file='~/Desktop/EHR-mining/BuildCohortDatasets/OtherScriptsAndData/filterCounts.Rdata')
i <- 1L
```
<br />

#### Figure 1. *E. coli* - CRO vs. TZP.
```{r, echo=FALSE}
build_flowchart(steps_df = filterCounts[[i]]$df, 
                final_split = filterCounts[[i]]$trt,
                title = names(filterCounts)[i]); i <- i + 1L
```
<br />
<br />

#### Figure 2. *K. pneumoniae* - CRO vs. TZP.
```{r, echo=FALSE}
build_flowchart(steps_df = filterCounts[[i]]$df, 
                final_split = filterCounts[[i]]$trt,
                title = names(filterCounts)[i]); i <- i + 1L
```
<br />
<br />

#### Figure 3. *P. mirabilis* - CRO vs. TZP.
```{r, echo=FALSE}
build_flowchart(steps_df = filterCounts[[i]]$df, 
                final_split = filterCounts[[i]]$trt,
                title = names(filterCounts)[i]); i <- i + 1L
```
<br />
<br />

#### Figure 4. *P. aeruginosa* - FEP vs. TZP.
```{r, echo=FALSE}
build_flowchart(steps_df = filterCounts[[i]]$df, 
                final_split = filterCounts[[i]]$trt,
                title = names(filterCounts)[i]); i <- i + 1L
```
<br />
<br />

#### Figure 5. *S. aureus* - OXA vs. CFZ.
```{r, echo=FALSE}
build_flowchart(steps_df = filterCounts[[i]]$df, 
                final_split = filterCounts[[i]]$trt,
                title = names(filterCounts)[i]); i <- i + 1L
```
<br />
<br />

#### Figure 6. *S. aureus* (MRSA) - VAN vs. switch to DAP.
```{r, echo=FALSE}
build_flowchart(steps_df = filterCounts[[i]]$df, 
                final_split = filterCounts[[i]]$trt,
                title = names(filterCounts)[i]); i <- i + 1L
```
<br />
<br />

#### Figure 7. *E. faecalis* - VAN vs. switch to AMP.
```{r, echo=FALSE}
build_flowchart(steps_df = filterCounts[[i]]$df, 
                final_split = filterCounts[[i]]$trt,
                title = names(filterCounts)[i]); i <- i + 1L
```
<br />
<br />

#### Figure 8. *E. faecium* (VRE) - DAP vs. LZD.
```{r, echo=FALSE}
build_flowchart(steps_df = filterCounts[[i]]$df, 
                final_split = filterCounts[[i]]$trt,
                title = names(filterCounts)[i]); i <- i + 1L
```
<br />
<br />





### Table 6. List of covariates available for each cohort.
```{r, echo=FALSE, out.width='500pt', fig.align='left'}
load(file = '~/Desktop/EHR-mining/BuildCohortDatasets/OtherScriptsAndData/covariates_cohort_matrix.Rdata')
kable(var_mat, "html", escape = TRUE) %>%
   kable_styling(full_width = FALSE, position='left')# %>%
#column_spec(extra_css = "word-wrap: break-word;")
```
<br />
<br />



### Tables 7-14. Covariate balance across treatment groups.
<br />

#### Table 7. *E. coli* - CRO vs. TZP.
```{r, echo=FALSE}
load(file = '~/Desktop/EHR-mining/BuildCohortDatasets/OtherScriptsAndData/table1s.Rdata')
idx <- 1L
kable(table1s[[idx]], "html", escape = TRUE) %>% kable_styling(position='left') %>% scroll_box(width='150%'); idx <- idx + 1L
```
<br />
<br />

#### Table 8. *K. pneumoniae* - CRO vs. TZP.
```{r, echo=FALSE}
kable(table1s[[idx]], "html", escape = TRUE) %>% kable_styling(position='left') %>% scroll_box(width='150%'); idx <- idx + 1L
```
<br />
<br />

#### Table 9. *P. mirabilis* - CRO vs. TZP.
```{r, echo=FALSE}
kable(table1s[[idx]], "html", escape = TRUE) %>% kable_styling(position='left') %>% scroll_box(width='150%'); idx <- idx + 1L
```
<br />
<br />

#### Table 10. *P. aeruginosa* - FEP vs. TZP.
```{r, echo=FALSE}
kable(table1s[[idx]], "html", escape = TRUE) %>% kable_styling(position='left') %>% scroll_box(width='150%'); idx <- idx + 1L
```
<br />
<br />

#### Table 11. *S. aureus* - OXA vs. CFZ.
```{r, echo=FALSE}
kable(table1s[[idx]], "html", escape = TRUE) %>% kable_styling(position='left') %>% scroll_box(width='150%'); idx <- idx + 1L
```
<br />
<br />

#### Table 12. *S. aureus* (MRSA) - VAN vs. switch to DAP.
```{r, echo=FALSE}
kable(table1s[[idx]], "html", escape = TRUE) %>% kable_styling(position='left') %>% scroll_box(width='150%'); idx <- idx + 1L
```
<br />
<br />

#### Table 13. *E. faecalis* - VAN vs. switch to AMP.
```{r, echo=FALSE}
kable(table1s[[idx]], "html", escape = TRUE) %>% kable_styling(position='left') %>% scroll_box(width='150%'); idx <- idx + 1L
```
<br />
<br />

#### Table 14. *E. faecium* (VRE) - DAP vs. LZD.
```{r, echo=FALSE}
kable(table1s[[idx]], "html", escape = TRUE) %>% kable_styling(position='left') %>% scroll_box(width='150%'); idx <- idx + 1L
```
<br />
<br />



### Tables 15-22. ATE estimation data.
<br />
```{r, echo=FALSE}
load(file='~/Desktop/EHR-mining/BuildCohortDatasets/CohortInfo/treatment/ATE_estimates_list.Rdata')
ATEs <- ATE_info$ATE
idx <- 1L
```


#### Table 15. *E. coli* - CRO vs. TZP.
```{r, echo=FALSE}
kable(ATEs[[idx]], "html", escape=TRUE, digits=3) %>% kable_styling(position='left'); idx <- idx + 1L
```
<br />
<br />

#### Table 16. *K. pneumoniae* - CRO vs. TZP.
```{r, echo=FALSE}
kable(ATEs[[idx]], "html", escape=TRUE, digits=3) %>% kable_styling(position='left'); idx <- idx + 1L
```
<br />
<br />

#### Table 17. *P. mirabilis* - CRO vs. TZP.
```{r, echo=FALSE}
kable(ATEs[[idx]], "html", escape=TRUE, digits=3) %>% kable_styling(position='left'); idx <- idx + 1L
```
<br />
<br />

#### Table 18. *P. aeruginosa* - FEP vs. TZP.
```{r, echo=FALSE}
kable(ATEs[[idx]], "html", escape=TRUE, digits=3) %>% kable_styling(position='left'); idx <- idx + 1L
```
<br />
<br />

#### Table 19. *S. aureus* - OXA vs. CFZ.
```{r, echo=FALSE}
kable(ATEs[[idx]], "html", escape=TRUE, digits=3) %>% kable_styling(position='left'); idx <- idx + 1L
```
<br />
<br />

#### Table 20. *S. aureus* (MRSA) - VAN vs. switch to DAP.
```{r, echo=FALSE}
kable(ATEs[[idx]], "html", escape=TRUE, digits=3) %>% kable_styling(position='left'); idx <- idx + 1L
```
<br />
<br />

#### Table 21. *E. faecalis* - VAN vs. switch to AMP.
```{r, echo=FALSE}
kable(ATEs[[idx]], "html", escape=TRUE, digits=3) %>% kable_styling(position='left'); idx <- idx + 1L
```
<br />
<br />

#### Table 22. *E. faecium* (VRE) - DAP vs. LZD.
```{r, echo=FALSE}
kable(ATEs[[idx]], "html", escape=TRUE, digits=3) %>% kable_styling(position='left'); idx <- idx + 1L
```





### Tables 23-30. CATE estimation data.
<br />
```{r, echo=FALSE}
load(file = '~/Desktop/EHR-mining/BuildCohortDatasets/CohortInfo/treatment/CATE_estimates_list.Rdata')
CATEs <- sapply(CATE_list, '[', 'ATEs')
for (i in seq_along(CATEs)) {
   CATEs[[i]] <- cbind('leaf' = seq_len(nrow(CATEs[[i]])), CATEs[[i]])
   rownames(CATEs[[i]]) <- NULL
}
idx <- 1L
```


#### Table 23. *E. coli* - CRO vs. TZP.
```{r, echo=FALSE, out.width='400pt', out.height='750pt', fig.align='center', include=TRUE}
kable(CATEs[[idx]], "html", escape=TRUE, digits=3) %>% kable_styling(position='left'); idx <- idx + 1L
```
<br />
<br />

#### Table 24. *K. pneumoniae* - CRO vs. TZP.
```{r, echo=FALSE}
kable(CATEs[[idx]], "html", escape=TRUE, digits=3) %>% kable_styling(position='left'); idx <- idx + 1L
```
<br />
<br />

#### Table 25. *P. mirabilis* - CRO vs. TZP.
```{r, echo=FALSE}
kable(CATEs[[idx]], "html", escape=TRUE, digits=3) %>% kable_styling(position='left'); idx <- idx + 1L
```
<br />
<br />

#### Table 26. *P. aeruginosa* - FEP vs. TZP.
```{r, echo=FALSE}
kable(CATEs[[idx]], "html", escape=TRUE, digits=3) %>% kable_styling(position='left'); idx <- idx + 1L
```
<br />
<br />

#### Table 27. *S. aureus* - OXA vs. CFZ.
```{r, echo=FALSE}
kable(CATEs[[idx]], "html", escape=TRUE, digits=3) %>% kable_styling(position='left'); idx <- idx + 1L
```
<br />
<br />

#### Table 28. *S. aureus* (MRSA) - VAN vs. switch to DAP.
```{r, echo=FALSE}
kable(CATEs[[idx]], "html", escape=TRUE, digits=3) %>% kable_styling(position='left'); idx <- idx + 1L
```
<br />
<br />

#### Table 29. *E. faecalis* - VAN vs. switch to AMP.
```{r, echo=FALSE}
kable(CATEs[[idx]], "html", escape=TRUE, digits=3) %>% kable_styling(position='left'); idx <- idx + 1L
```
<br />
<br />

#### Table 30 *E. faecium* (VRE) - DAP vs. LZD.
```{r, echo=FALSE}
kable(CATEs[[idx]], "html", escape=TRUE, digits=3) %>% kable_styling(position='left'); idx <- idx + 1L
```





